Results

### 2024-02-24 Sections/Results.qmd
remove code from main Sections

---
title: "Results"
author: "Thomas Gorman"
format: 
  html:
    toc: true
    toc-depth: 5
    toc-expand: true
    number-sections: true
    number-depth: 5
    strip-comments: true
#toc: true
# toc-title: Contents
# toc-depth: 4
# toc-expand: 1
# execute:
#   echo: false
---

>>>>

---
title: "Results"
author: "Thomas Gorman"
toc: true
toc-depth: 5
toc-expand: true
number-sections: true
number-depth: 5
strip-comments: true
echo: false
#toc: true
# toc-title: Contents
# toc-depth: 4
# toc-expand: 1
# execute:
#   echo: false
---
